Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-03-16 Cost_manuscript.Rmd
successfully combined both preregs. pdf not knitting, but word doc is

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1^2 & Joseph T. McGuire^1^2"
csl: apa.csl
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
  word_document: default #reference_docx: Style_reference_draft.docx
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
#bibliography: mPFC_paper.bib
---

@@

```{r Load data for between-subject experiment, echo = FALSE}
### data loading and cleaning up
# forced travels are switched to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
# The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
setwd("./Cost2/data")
files <- dir(pattern = '_log.csv')

@@

# load the data and remove extreme subjects
dataWth <- data_frame(SubjID = files) %>% 
  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
  mutate(SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(RT = ifelse(RT > 10.1, 10, RT),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Btype = BlockType) %>%
  unite(Cost, Cost, BlockType) %>%
  rename(TrialN = X1) %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
                           Cost == "COGNITIVE_0" ~ "Cognitive",
                           Cost == "GRIP_1" ~ "Physical",
                           Cost == "WAIT_1" ~ "Wait_P")) %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))

@@

### Analyses

@@

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = cols) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = cols) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

@@

``` {r WTH: 16.2.1. Overall Proportion diffs, fig.align = "center", fig.width = 6, fig.height = 4, echo = FALSE}  
# ## ECDF of proportion completed per cost type
# temp <- dataWth %>%
#         filter(Choice < 2) %>%
#         #mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait_0", "Wait_1"))) %>%
#         group_by(SubjID, Cost) %>%
#         summarise(pComplete = mean(Choice))
# 
# 
# # plots
# (p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
#         geom_boxplot(show.legend = F) +
#         scale_fill_manual(values = cols) +
#         ylim(c(0, 1)) +
#         labs(y = "Proportion Completed") +
#         theme(panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank(), 
#             panel.background = element_blank(), 
#             axis.line = element_line(colour = "black"),
#             text = element_text(size = 16)))

@@

# plot proportion accepted per trial/offer combo
(n2 <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = cols) +
          scale_fill_manual(values = cols) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22)))

@@

``` {r WTH: 16.3.1., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# Proportion of forced travels per subject and cost type
propFails <- dataWth %>%
  filter(Cost != "WAIT") %>%
  group_by(SubjID, Cost) %>%
  summarise(propFails = mean(rawChoice == 2)) %>%
  group_by(Cost) %>%
  summarise(meanQuit = mean(propFails))
# 
# # Reaction times ECDFs including offer and in-trial quits
# (RTs <- data %>%
#   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
#   filter(rawChoice < 2) %>% 
#   ggplot(aes(RT, color = Cost)) + 
#     #stat_ecdf(lwd = 1.2) +
#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
#     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
#     scale_color_manual(values = cols) +
#     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
#     labs(x = "Time in Cost", y = "Proportion Completed") +
#     theme(panel.grid.major = element_blank(),
#       panel.grid.minor = element_blank(),
#       panel.background = element_blank(),
#       axis.line = element_line(colour = "black"),
#       text = element_text(size = 16)))

@@

autoplot(survData) +
  geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(12)) +
  ylim(0, 1) +
  scale_x_continuous(breaks = seq(0, 12), labels = seq(-2, 10)) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = c(0.35, 0.2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 22))

@@

``` {r WTH: 16.3.3. plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# various plots
# acceptances across blocks
propBlocks <- dataWth %>%
    filter(Choice < 2) %>%
    group_by(SubjID) %>%
    mutate(Block = case_when(
      Block %in% c(1, 2) ~ 1,
      Block %in% c(3, 4) ~ 2,
      Block %in% c(5, 6) ~ 3
    )) %>%
    group_by(SubjID, Cost, Block) %>%
    summarise(propAccept_subj = mean(Choice)) %>%
    group_by(Cost, Block) %>%
    summarize(propAccept = mean(propAccept_subj),
              seAccept = sd(propAccept_subj)/sqrt(nSubjs_wth)) %>%
    ggplot(aes(Block, propAccept, color = Cost)) +
      geom_point(size = 2) +
      geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
      geom_line() +
      ylim(0, 1) +
      labs(y = "Proportion Accepted") +
      scale_x_continuous(breaks = c(1, 2, 3)) +
      scale_color_manual(values = cols) +
      scale_fill_manual(values = cols) +
      theme(legend.key = element_blank(),
         legend.position = c(0.8, 0.25),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"),
         text = element_text(size = 16))

@@

mid <- dataWth %>%
  filter(Choice < 2, !(Block %in% c(3,4))) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
            propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
  ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
    geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
    labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
    scale_fill_manual(values = cols) +
    scale_color_manual(values = cols) +
    xlim(0, 1) +
    ylim(0, 1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
    geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
    theme(legend.key = element_blank(),
       legend.position = c(0.8, 0.25),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.background = element_blank(),
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))

# wait vs effort across effort conditions
pAll <- dataWth %>%
  filter(Choice < 2) %>%
  mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
         BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
  group_by(SubjID, BlockType) %>%
  summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
            Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
  ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
    geom_point(size = 5, show.legend = T) +
    xlim(0,1) +
    ylim(0,1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    theme_classic()

@@

# plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
# lines connect the same subject between the blocks
dataWth %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
         Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
  spread(Type, Diffscore) %>%
  ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
    geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
    scale_fill_manual(values = cols) +
    annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
    annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
    annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
    annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
    labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
    ylim(-0.7, 0.7) +
    xlim(-0.7, 0.7) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.35),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 20))

@@

# # this helps make sense of the toal earnings
# # plotting mean earnings per cost and block
# dataWth %>%
#   filter(rawChoice == 1) %>%
#   group_by(SubjID) %>%
#   mutate(Block = case_when(
#     Block %in% c(1, 2) ~ 1,
#     Block %in% c(3, 4) ~ 2,
#     Block %in% c(5, 6) ~ 3
#   )) %>%
#   group_by(SubjID, Cost, Block) %>%
#   summarise(subEarnings = sum(Offer)) %>%
#   group_by(Cost, Block) %>%
#   summarise(meanEarned = mean(subEarnings),
#             seEarned = sd(subEarnings) / sqrt(nSubjs_wth)) %>%
#   ggplot(aes(Block, meanEarned, color = Cost)) +
#     geom_point(size = 2) +
#     geom_errorbar(aes(ymin = meanEarned - seEarned, ymax = meanEarned + seEarned, color = Cost), width = 0.1, size = 1.5) +
#     geom_line(size = 1.5) +
#     labs(y = "Mean Earnings +- SE (cents)") +
#     scale_x_continuous(breaks = c(1, 2, 3)) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     theme(legend.key = element_blank(),
#           #legend.position = c(0.1, 0.8),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(),
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

@@

# more prepost tests
# diffscore prepost for effort vs wait
dataWth %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  spread(Cost, Diffscore) %>%
  ggplot() +
    geom_point(aes(Cognitive, Wait_C), color = cols[1]) +
    geom_point(aes(Physical, Wait_P), color = cols[2]) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ylim(-0.5, 0.5) +
    xlim(-0.5, 0.5) +
    #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    #geom_boxplot(show.legend = F, size = 1.5) +
    #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
    #scale_color_manual(values = cols) +
    #scale_fill_manual(values = cols) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))

>>>>

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1^2 & Joseph T. McGuire^1^2"
csl: apa.csl
output:
  word_document: default #reference_docx: Style_reference_draft.docx
  pdf_document:
    highlight: haddock
    keep_tex: no
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
#bibliography: mPFC_paper.bib
---

@@

```{r Load data for between-subject experiment, echo = FALSE}
### data loading and cleaning up
# forced travels are switched to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
# The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
setwd("./Cost2/data")
files <- dir(pattern = '_log.csv')

@@

# load the data and remove extreme subjects
dataWth <- data_frame(SubjID = files) %>% 
  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
  mutate(SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(RT = ifelse(RT > 10.1, 10, RT),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Btype = BlockType) %>%
  unite(Cost, Cost, BlockType) %>%
  rename(TrialN = X1) %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
                           Cost == "COGNITIVE_0" ~ "Cognitive",
                           Cost == "GRIP_1" ~ "Physical",
                           Cost == "WAIT_1" ~ "Wait_P"),
         Cost = as.factor(Cost)) %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))

@@

@@

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsWth) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsWth) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

@@

``` {r WTH: 16.2.1. Overall Proportion diffs, fig.align = "center", fig.width = 6, fig.height = 4, echo = FALSE}  
# ## ECDF of proportion completed per cost type
# temp <- dataWth %>%
#         filter(Choice < 2) %>%
#         #mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait_0", "Wait_1"))) %>%
#         group_by(SubjID, Cost) %>%
#         summarise(pComplete = mean(Choice))
# 
# 
# # plots
# (p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
#         geom_boxplot(show.legend = F) +
#         scale_fill_manual(values = colsWth) +
#         ylim(c(0, 1)) +
#         labs(y = "Proportion Completed") +
#         theme(panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank(), 
#             panel.background = element_blank(), 
#             axis.line = element_line(colour = "black"),
#             text = element_text(size = 16)))

@@

# plot proportion accepted per trial/offer combo
(n2 <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = colsWth) +
          scale_fill_manual(values = colsWth) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22)))

@@

``` {r WTH: 16.3.1., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# Proportion of forced travels per subject and cost type
propFails <- dataWth %>%
  filter(Cost != "WAIT") %>%
  group_by(SubjID, Cost) %>%
  summarise(propFails = mean(rawChoice == 2)) %>%
  group_by(Cost) %>%
  summarise(meanQuit = mean(propFails))
# 
# # Reaction times ECDFs including offer and in-trial quits
# (RTs <- data %>%
#   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
#   filter(rawChoice < 2) %>% 
#   ggplot(aes(RT, color = Cost)) + 
#     #stat_ecdf(lwd = 1.2) +
#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
#     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
#     scale_color_manual(values = colsWth) +
#     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
#     labs(x = "Time in Cost", y = "Proportion Completed") +
#     theme(panel.grid.major = element_blank(),
#       panel.grid.minor = element_blank(),
#       panel.background = element_blank(),
#       axis.line = element_line(colour = "black"),
#       text = element_text(size = 16)))

@@

autoplot(survData) +
  geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = colsWth) +
  scale_fill_manual(values = colsWth) +
  scale_x_continuous(breaks = seq(12)) +
  ylim(0, 1) +
  scale_x_continuous(breaks = seq(0, 12), labels = seq(-2, 10)) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = c(0.35, 0.2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 22))

@@

``` {r WTH: 16.3.3. plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# various plots
# acceptances across blocks
propBlocks <- dataWth %>%
    filter(Choice < 2) %>%
    group_by(SubjID) %>%
    mutate(Block = case_when(
      Block %in% c(1, 2) ~ 1,
      Block %in% c(3, 4) ~ 2,
      Block %in% c(5, 6) ~ 3
    )) %>%
    group_by(SubjID, Cost, Block) %>%
    summarise(propAccept_subj = mean(Choice)) %>%
    group_by(Cost, Block) %>%
    summarize(propAccept = mean(propAccept_subj),
              seAccept = sd(propAccept_subj)/sqrt(nSubjs_wth)) %>%
    ggplot(aes(Block, propAccept, color = Cost)) +
      geom_point(size = 2) +
      geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
      geom_line() +
      ylim(0, 1) +
      labs(y = "Proportion Accepted") +
      scale_x_continuous(breaks = c(1, 2, 3)) +
      scale_color_manual(values = colsWth) +
      scale_fill_manual(values = colsWth) +
      theme(legend.key = element_blank(),
         legend.position = c(0.8, 0.25),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"),
         text = element_text(size = 16))

@@

mid <- dataWth %>%
  filter(Choice < 2, !(Block %in% c(3,4))) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
            propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
  ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
    geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
    labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
    scale_fill_manual(values = colsWth) +
    scale_color_manual(values = colsWth) +
    xlim(0, 1) +
    ylim(0, 1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
    geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
    theme(legend.key = element_blank(),
       legend.position = c(0.8, 0.25),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.background = element_blank(),
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))

# wait vs effort across effort conditions
pAll <- dataWth %>%
  filter(Choice < 2) %>%
  mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
         BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
  group_by(SubjID, BlockType) %>%
  summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
            Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
  ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
    geom_point(size = 5, show.legend = T) +
    xlim(0,1) +
    ylim(0,1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    scale_color_manual(values = colsWth) +
    scale_fill_manual(values = colsWth) +
    theme_classic()

@@

# plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
# lines connect the same subject between the blocks
dataWth %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
         Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
  spread(Type, Diffscore) %>%
  ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
    geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
    scale_fill_manual(values = colsWth) +
    annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
    annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
    annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
    annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
    labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
    ylim(-0.7, 0.7) +
    xlim(-0.7, 0.7) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.35),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 20))

@@

# # this helps make sense of the toal earnings
# # plotting mean earnings per cost and block
# dataWth %>%
#   filter(rawChoice == 1) %>%
#   group_by(SubjID) %>%
#   mutate(Block = case_when(
#     Block %in% c(1, 2) ~ 1,
#     Block %in% c(3, 4) ~ 2,
#     Block %in% c(5, 6) ~ 3
#   )) %>%
#   group_by(SubjID, Cost, Block) %>%
#   summarise(subEarnings = sum(Offer)) %>%
#   group_by(Cost, Block) %>%
#   summarise(meanEarned = mean(subEarnings),
#             seEarned = sd(subEarnings) / sqrt(nSubjs_wth)) %>%
#   ggplot(aes(Block, meanEarned, color = Cost)) +
#     geom_point(size = 2) +
#     geom_errorbar(aes(ymin = meanEarned - seEarned, ymax = meanEarned + seEarned, color = Cost), width = 0.1, size = 1.5) +
#     geom_line(size = 1.5) +
#     labs(y = "Mean Earnings +- SE (cents)") +
#     scale_x_continuous(breaks = c(1, 2, 3)) +
#     scale_color_manual(values = colsWth) +
#     scale_fill_manual(values = colsWth) +
#     theme(legend.key = element_blank(),
#           #legend.position = c(0.1, 0.8),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(),
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

@@

# more prepost tests
# diffscore prepost for effort vs wait
dataWth %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  spread(Cost, Diffscore) %>%
  ggplot() +
    geom_point(aes(Cognitive, Wait_C), color = colsWth[1]) +
    geom_point(aes(Physical, Wait_P), color = colsWth[2]) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ylim(-0.5, 0.5) +
    xlim(-0.5, 0.5) +
    #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    #geom_boxplot(show.legend = F, size = 1.5) +
    #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
    #scale_color_manual(values = colsWth) +
    #scale_fill_manual(values = colsWth) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))

# diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
dataWth %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  ggplot(aes(Cost, Diffscore, fill = Cost)) +
    geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    geom_boxplot(show.legend = F, size = 1.5) +
    geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
    scale_color_manual(values = colsWth) +
    scale_fill_manual(values = colsWth) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))
```
